openTSNE: a modular Python library for t-SNE dimensionality reduction and embedding

### 2021-03-17 paper/policar2020-opentsne.tex
emails
grant info

\author{
  Pavlin G. Poli\v{c}ar\textsuperscript{1}\\
  \texttt{pavlin.policar@fri.uni-lj.si}\\
  \and
  Martin Stra\v{zar}\textsuperscript{2}\\
  \and
  Bla\v{z} Zupan\textsuperscript{1,3}\\
}

@@

\section*{Competing interests}
The authors declare that they have no competing interests.

@@

\section*{Acknowledgements}
We want to thank Dmitry Kobak for various helpful discussions and best practices
when using t-SNE and his contributions to the source code. We would also
like to thank George Linderman for his help with the FIt-SNE algorithm.

>>>>

\author{
  Pavlin G. Poli\v{c}ar\textsuperscript{1}\\
  \texttt{pavlin.policar@fri.uni-lj.si}\\
  \and
  Martin Stra\v{zar}\textsuperscript{2}\\
  \texttt{martin.strazar@gmail.com}\\
  \and
  Bla\v{z} Zupan\textsuperscript{1,3}\\
  \texttt{blaz.zupan@fri.uni-lj.si}\\
}

@@

\section*{Competing interests}
The authors declare no competing interests.

@@

\section*{Acknowledgements}
This work was supported by Slovenian Research Agency (P2-0209).
We want to thank Dmitry Kobak for various helpful discussions and best practices
when using t-SNE and his contributions to the source code. We would also
like to thank George Linderman for his help with the FIt-SNE algorithm.
